Conference Paper Title*

### 2020-03-15 paper.tex
Modify listing indent

\begin{lstlisting}[caption={Update encrypt key}, label={lst:key_exchange}, frame=single]
    function addEncryptKey(
        address _subscriber,
        string memory _encryptKey
    ) public {
        require(
            msg.sender == provider,
            "Only provider can add blindedKey."
        );
        require(
            subscriber2Purchase[_subscriber].isKeyAdded == false,
            "One encryptKey has been added."
        );
        subscriber2Purchase[_subscriber].encryptKey = _encryptKey;
        subscriber2Purchase[_subscriber].isKeyAdded = true;
        emit newEncryptKey(_subscriber, _encryptKey);
    }
\end{lstlisting}

>>>>

\begin{lstlisting}[caption={Update encryption key}, label={lst:key_exchange}, frame=single]
function addEncryptKey(
  address _subscriber,
  string memory _encryptKey
) public {
  require(
      msg.sender == provider,
      "Only provider can add blindedKey."
  );
  require(
      subscriber2Purchase[_subscriber].isKeyAdded == false,
      "One encryptKey has been added."
  );
  subscriber2Purchase[_subscriber].encryptKey = _encryptKey;
  subscriber2Purchase[_subscriber].isKeyAdded = true;
  emit newEncryptKey(_subscriber, _encryptKey);
}
\end{lstlisting}
